### 2021-12-01 paper_review/response_1.txt

RESPONSE
----------
> Thank you for these important points of feedback.
>
> The Sun has been included to clarify the direction along which
> parallax uncertainties are expected to produce erroneous
> clusterings (analogous to the "Fingers of God" effect in the
> extragalactic literature).  This is relevant because the HDBScan
> clustering method used by Kounkel & Covey in their 2019 paper
> likely was susceptible to this systematic effect.  A sentence has
> been added to the caption of Figure 1 to clarify this point.
> 
> The {X,Y}, {Z,X}, and {Z,Y} panels are plotted at different scales
> in order to keep the aspect ratios roughly correct.  The reported
> KC2019 cluster members span {ΔX, ΔY, ΔZ} of roughly {400, 600, 200}
> parsecs,  which grows to ~{600, 600, 200} parsecs when including
> the Sun.  The {Z,X} and {Z,Y} panels should therefore roughly have
> aspect ratios of 1:3 in order for the parsec to not be stretched
> too much in either dimension.  The top-down {X,Y} view is the most
> informative dimension, which is why it is enlarged related to the
> edge-on views (and its 1:1 aspect ratio is set by the same
> consideration).
>
> Finally, the tangential velocities are important because they tell
> us whether the structures are kinematically coherent.  Open
> clusters typically have velocity dispersions of order ~1km/s.
> Meingast et al. 2021 (A&A 645 84) for instance suggest tangential
> velocities <2 km/s (from the mean cluster velocity) as a plausible
> cutoff for selecting candidate cluster members.  One needs to
> compute these as relative tangential velocities instead of just
> looking at the proper motions because the proper motions are
> changed by line-of-sight projection effects, especially when the
> clusters appear stretched over tens of degrees on-sky.  See for
> instance Figure 2 of Meingast+2021, or Figure 14 of Bouma+2021 (AJ,
> 162, 197).  In our case, the tangential velocities indicate that
> the spread in Kounkel & Covey 2019's reported cluster members is
> ~10km/s, which is large enough that it does not make obvious
> kinematic sense to consider all of these stars to be part of the
> same structure.
>
> We've added a few sentences in the manuscript to clarify these
> latter points.

@@

REVIEWER COMMENT
----------
Figure 3 bottom: Can the IC 2602 and 2391 rotation periods be added
to this plot? Lines 276-278 mention that these and cite Douglas et
al. 2021 (although the reference does not seem to be complete). Isn't
it interesting that the interlopers all fall on the Praesepe rotation
sequence?

RESPONSE
----------
> Thank you for pointing out the missing link in the reference to
> Douglas et al. 2021, which should have pointed to
> https://ui.adsabs.harvard.edu/abs/2021tsc2.confE.157D/abstract, and
> has been updated in the revision.  The rotation periods from this
> work, which includes IC 2602, IC 2391, and a few other 30-50 Myr
> clusters, are not yet public.  
>
> The interlopers falling on the Praesepe sequence is indeed a bit
> odd, but it's really only ~3-5 stars. A much bigger set of
> interlopers didn't have detected rotation periods at all! (See
> final paragraph of Section 2.2.2).  At the other reviewer's
> request, we've also added a sentence noting that some of these
> stars might be unresolved F+K binaries.

@@

REVIEWER COMMENT
----------
p 5 lines 258-261: rather than simply throw the TESS values out in
favor of the Kepler ones, the authors should compare them to evaluate
the accuracy and reliability of the TESS values.

RESPONSE
----------
> Thank you for this point -- please see kepler_vs_tess_prot.png in
> the attached, which shows the 28 referenced stars that overlap.  5
> of the 28 stars have Kepler rotation periods above 10 days, of
> which none were correctly recovered by TESS (3 are chosen at the
> half-period harmonic).  Of the 23 stars with periods below 10 days,
> 21 of the TESS periods agree with the Kepler rotation periods, and
> 2 are at the double-period harmonic.
>
> We've updated the text to reflect this point, which doesn't affect
> any of the conclusions given that almost all the δ Lyr cluster
> stars have rotation periods below below 10 days.

@@

The significance of this slope is unclear and a sigma is not a good
way to evaluate it. Perform a ratio of chi-squared or F-test to
evaluate it vs. a flat line.

RESPONSE
----------
> TODO ??? WHY ISN'T SIGMA OK?  THE POINT IS THAT IT'S 2-SIGMA...

REVIEWER COMMENT
----------
Lines 530-542: does option (ii) include a transit fit as well? I
assume it does but it would be good to clarify. And is option (i) the
2nd and 4th order polynomial? Perhaps just state this?

RESPONSE
----------
> Yes, option (ii) includes the transit -- we've updated this in the
> text for clarity.
>
> Yes, option (i) is the 2nd or 4th order polynomial.  We've updated
> the text to state this more directly as well.  Thank you!

@@

RESPONSE
----------
> Yes -- we've added this to the text.  Thank you.

REVIEWER COMMENT
----------
Section 4.2

Analysis of the motion of the photocentroid has been widely used to
help validate Kepler planets. Can this be used here to distinguish
between the possible A and B host stars?

RESPONSE
----------
> Kepler-1627B is ~0.16 arcseconds East of Kepler-1627A.  For the
> sake of argument, assume it contributes 2% of the flux to the
> aperture (an overestimate), and neglect other stars in the scene. 
>
> Taking the origin at Kepler-1627A, the center of light outside of
> transit is then roughly (0.98*0 arcsec + 0.02*0.16 arcsec) = 0.0032
> arcsec due East of the primary.
>
> During transit, if the transit happens on the primary, the center
> of light is roughly ( (0.98-0.002)*0 arcsec + (1-(0.98-0.002))*0.16
> arcsec ) = 0.0035 arcsec due East of the primary -- i.e., it is
> closer to the secondary by 0.3 milliarcseconds, since the primary
> is getting fainter.
>
> If the transit instead happened on the secondary, the center of
> light would be roughly (0.98*0 arcsec + (0.9*0.02)*0.16 arcsec) ~=
> 0.00288 arcsec due East of the primary, where a 10% intrinsic
> eclipse depth on the secondary is required to fit the observed
> transit depth.  In this scenario, the centroid would shift closer
> to the *primary* by 0.3 milliarcseconds.
>
> Examining the NASA SPOC Data Validation Report (DVR), there are two
> available photocentroid tests, the first based on the flux-weighted
> centroid analysis, and the second based on the difference image
> centroid offset test.  The latter test yields offset uncertainties
> of ~100 milliarcsec for Kepler-1627, which is far above the
> relevant signal.  The former test yields centroid peak RA and DEC
> offsets consistent with zero, with uncertainties of 0.9 and 1.1
> milliarcsec respectively (page 19 of 552 in the DR25 DVR).  So,
> given that the quoted centroid precision uncertainties are a factor
> of ~3 larger than the expected shift, it is not possible to use the
> test in a way that distinguishes the two host stars in a
> statistically convincing way.

@@

REVIEWER COMMENT
----------
Line 604-608: The statement that the density from the transit
duration is inconsistent with that expected for the M dwarf "B" cites
Table 2 and Choi+2016, but that Table does not appear to provide any
information on "B", and the Choi+2016 reference is just for the Mesa
models. A density of 2 g/cm3 (or lower) is possible for an M dwarf on
the pre-main sequence, depending on the mass, age and model used.

RESPONSE
----------
> Thank you for catching this -- this citation is indeed deprecated
> and erroneously was not updated during the writing process.  The
> final adopted calculation was based on the masses and radii from
> the Baraffe+2015 models, rather than the MESA models (Choi+2016).
> The Baraffe models are available from
> http://perso.ens-lyon.fr/isabelle.baraffe/BHAC15dir/BHAC15_tracks+structure.
>
> We believe that the companion's mass is roughly between 0.3 and 0.4
> Msun, and that the age of the system is ~38 +/- 6 Myr.  The Baraffe
> models give:
>
>    32 Myr 0.300 Msun, 0.481 Rsun, 3.80 g / cm3
>    35 Myr 0.300 Msun, 0.465 Rsun, 4.21 g / cm3
>    40 Myr 0.300 Msun, 0.443 Rsun, 4.86 g / cm3
>    32 Myr 0.400 Msun, 0.555 Rsun, 3.30 g / cm3
>    35 Myr 0.400 Msun, 0.537 Rsun, 3.64 g / cm3
>    40 Myr 0.400 Msun, 0.514 Rsun, 4.15 g / cm3
>    32 Myr 0.330 Msun, 0.506 Rsun, 3.60 g / cm3
>    35 Myr 0.330 Msun, 0.489 Rsun, 3.98 g / cm3
>    40 Myr 0.330 Msun, 0.467 Rsun, 4.58 g / cm3
>
> i.e., our default assumption was 40 Myr and 0.33 Msun.  The age is
> adopted for the reasons discussed in the text.  The mass is based
> off the observed deltaMag in 832nm and K' (3.14 +/- 0.15 and 2.37
> +/- 0.02 respectively), which implies absolute magnitudes for the
> secondary of K'=XXX and [832]=YYY.  Based on a set of absolute
> magnitude and color relations from a submitted paper by A. Kraus,
> these gave ~=0.33 Msun.  (TODO: NEED TO BEEF THIS UP!)
>
> The plausible range of companion densities is therefore 3.30 g/cc
> to 4.86 g/cc.  We've updated the text to reflect this uncertainty,
> but it doesn't change the overall point that our measured stellar
> density (2.00+/-0.24 g/cc) is still a fair bit lower than the
> expected range.

TODO TODO REMOVE THIS
> As a sanity check, these calibrations find that for a companion
> spectral type of M2.5, one expects colors of G-K'=3.39 mag and
> G-[832] = 1.51 mag, though we cannot test this since Gaia DR2/EDR3
> does not resolve the secondary.
>
> For the primary spectral type of G8, one expects G-K'=1.58 mag and
> G-[832] = 0.71 mag (i.e., K'=13.02-1.58=11.44, and
> [832]=G-0.71=12.31 for the primary).  So it holds together
> (bolstering the case for it being a bound companion) to find
> DeltaK' = 2.37 mag and Delta[832] = 3.14 mag.

G8V: M_G = 5.098
M2.5V: M_G = 9.67 (ZAMS).
-> delta G = 9.67 - 5.098 = 4.57, so G =13.02+4.57= 17.592 for secondary
-> G-K'=3.39mag implies K' = 14.20 for secondary
-> G-[832]=1.51mag implies [832] = 16.08 for secondary
->
-> expected delta K' = 2.76
-> expected delta 832 = 3.78
.. (both are observed a bit lower!  i.e., it's not red enough)

@@

REVIEWER COMMENT
----------
Lines 613-614: it would be good to quantify this, i.e. how faint an
unresolved companion or background star must be based on the star's
position in the CMD.

RESPONSE
----------
> Visually, one can see that the width of the single-star sequence of
> δ Lyr candidates (black points) in the upper-right panel of Figure
> 3 is <~0.2 mag.  So, if we saw a star with the same (BP-RP) color
> as Kepler 1627 that were
> >~0.3 mag brighter in M_G, we would classify it as a likely
> >photometric
> binary.  This means we are able to exclude stars ~0.32* as bright
> as the primary (in Gaia G-band). This corresponds to excluding
> bound companions more massive than ~0.85 Msun (the primary's mass
> is ~0.95 Msun).  The SB2 tests do much better if the velocity
> separation exceeds the CCF width (down to 1% as bright as the
> primary;
> https://ui.adsabs.harvard.edu/abs/2015AJ....149...18K/abstract).
> For brevity, we would prefer to not present this information in the
> text.

@@

REVIEWER COMMENT
----------
Lines 635-638: Here, new observations appear for the first time but
are not described. While the details are given in the appendix, and
the outcome of the observations doesn't define this work, the authors
need to give some basic description of the observations, e.g.
passbands, SNR, resolution, observation times, etc. The authors
should not assume the reader actually know what HIRES and MuSCAT are!

RESPONSE
----------
> Thank you for this suggestion.  The main text now reads
>
> "We observed a transit of Kepler-1627 Ab on the night of 2021 Aug 7
> spectroscopically with HIRES at the Keck-I telescope and
> photometrically in $griz$ bands with MuSCAT3 at Haleakal\=a
> Observatory.  Details of the observation sequence are discussed in
> Appendix C; Figure 7 shows the results."
>
> The first paragraph of Appendix C has been significantly modified
> to include the requested additional information, including the
> passbands, exposure times, S/N, and instrument resolution.
> Regarding observation times, "the night of 2021 Aug 7" is
> sufficiently precise for the purposes of the text; Tables 5 and 6
> have the BJD-TDB timestamps for those who desire greater precision.

@@

REVIEWER COMMENT
----------
Section 5

line 670: assuming that SNR is not to blame, the problem is not
precision, the problem is either measuremnt systematics or
astrophysical noise.

RESPONSE
----------
> Thank you for this point; we've updated the text to say
> "signal-to-noise" rather than "precision".

@@

REVIEWER COMMENT
----------
line 678-683: The Ca II HK activity indicator "S" as well as the
H-alpha equivalent width could be obtained from the HIRES spectrum.
Have the authors checked fora X-ray or UV (Galex) detection of this
star? The star is likely not detected but its worth a look. In the
same vein, the authors may wish to comment on whether the star's
infrared emission indicates or rule out a substantial debris disk --
the star is detected in WISE (and perhaps Spitzer?)

RESPONSE
----------
> Regarding the S-values, they are shown in the second panel of
> Figure 7, and are also reported in Table 6.  The line profile
> changes shown in Figure 12 suggested that the majority of the RV
> variation observed was due to starspot-induced variations.
> Quantitative measurements of the H-alpha EWs are not expected to
> change this picture, and so we opt to not include them.
>
> Regarding the NIR, UV, and X-ray detections, we searched Vizier
> within a radius of 4 arcseconds.
>
> For the X-ray (i.e., ROSAT), there were no reported detections in
> Vizier.
>
> For the NIR and the possibility of a debris disk, Kepler-1627 is
> detected in W1, W2, W3, and W4 (see
> kepler1627_vizier_photometry.png attached).  While W4 might be in
> excess of the usual Rayleigh-Jeans tail, and this could be
> quantified by fitting synthetic stellar atmospheres, this type of
> analysis is best done at the population level, particularly given
> the calibration uncertainties that are present in W4 (e.g., Cotten
> & Song 2016, ApJS 225 15).  Since Kepler-1627 has not been
> identified as even a candidate debris disk host in the previous
> literature that performs these population-level infrared excess
> analyses, we opt to not speculate on this topic.
>
> For the UV, Olmedo+2015 reported a coincident source with NUVmag of
> 19.052 +/- 0.017 [AB mags], with a NUV S/N of 65 (2015, ApJ, 813,
> 100). Loyd et al 2020 similarly report a NUV flux of 4e-13 +/-
> 4e-15 mW/m^2, though the latter value is based on the same
> GALEX-CAUSE Kepler survey data presented by Olmedo+2015.  UV
> detections can sometimes be used as a youth indicator (e.g., Figure
> 9 of Newton+2021 AJ 161 65, which Newton et al attribute from the
> idea in Shkolnik+2011, ApJ 727 6).  For Kepler-1627, we have 2MASS
> J = 11.690+/-0.021, and therefore m_NUV-m_J = 7.36.  Given the Gaia
> (BP-RP)0 of 0.977, comparing to Figure 9 of Newton+2021 we find
> that Kepler-1627 overlaps with late-G type stars in Psc-Eri, the
> Pleiades, and the Hyades.  In other words, the UV flux is not a
> particularly strong diagnostic of the age for Kepler-1627 as an
> individual star.  It may well be worth exploring the GALEX-CAUSE
> Kepler survey data for the delta Lyr cluster generally, since the
> later type K and M dwarfs are expected to be elevated with respect
> to the Pleiades and Hyades sequences.  However, this goes beyond
> the scope of the present work, and the combination of the cluster
> membership, stellar rotation, stellar lithium content, and stellar
> activity all point to an age consistent with that reported in our
> work.

@@

REVIEWER COMMENT
----------
lines 699-701 It could be mentioned here that the planet orbital
period and stellar rotational period are not a rational combination.

RESPONSE
----------
> Done, thank you.

REVIEWER COMMENT
----------
line 723-726: The caveat that should be mentioned here is that this
is for older, main sequence stars.

RESPONSE
----------
> The first reviewer had a similar comment -- our response is the
> same:
>
> These completeness statistics were computed using KeplerPORTS (the
> Burke & Catanzarite 2021 citation).  KeplerPORTS corrects for red
> noise in the light curves by using the CDPP over different
> timescales -- see Section 3.3 of Burke, C. J. & Catanzarite, J.
> 2017, Planet Detection Metrics: Per-Target Detection Contours for
> Data Release 25, KSCI-19111-002.  This correction is performed
> using both a) the slope of the RMS CDPP versus transit duration for
> for "long" transit durations (the average of 7.5, 9.0, 10.5, 12.0,
> 12.5, and 15.0 hours) and b) the same slope for "short" transit
> durations (2.0, 2.5, 3.0, 3.5, and 4.5 hours). We retrieved these
> values from the DR25 Kepler occurrence rate products hosted on the
> NASA Exoplanet Archive.  For Kepler 1627, they were CDPP_long =
> 0.25478 and CDPP_short=0.79505.  Per Figure 2 of the KSCI-19111-002
> memo, these do indeed indicate a noisy star -- no surprises.
>
> We've added a sentence to the manuscript to clarify that we are
> talking about per-target detection contours, which should correct
> for the impact of at least the fast rotation period, inasmuch as it
> manifests in the slope of the CDPP versus transit duration.  We
> have also modified the wording for clarity, and have added a
> citation to Burke & Catanzarite's 2017 KSCI-19111-002 memo.
>
> To determine whether this CDPP-slope detection efficiency
> correction is *accurate* given the exact red-noise properties of
> Kepler-1627 (i.e., the rotation and flares), a full
> injection-recovery analysis of the light curve with a pipeline of
> our own would be necessary. This effort is outside our scope, for
> now.
